\texttt{apt-p2p}: A Peer-to-Peer Distribution System for Software Package Releases and Updates

### 2009-01-21 docs/paper/paper.tex
Final version of INFOCOM paper.

\begin{abstract}
The Internet has become a cost-effective
vehicle for software development and release, particular in the free software community.
Given the free nature of these software, there are often a number of users
motivated by altruism to help out with the distribution, so as to promote the healthy development
of this voluntary society. It is thus naturally expected that peer-to-peer distribution can be implemented,
which scale well with large user bases and can easily explore the network resources made available by
the volunteers.

Unfortunately, this application scenario has many unique characteristics, which
make a straightforward adoption of existing peer-to-peer systems for file sharing such as BitTorrent suboptimal. In particular,
a software release often consists of a large number of packages, which are difficult to be distributed individually, but the archive is
too large to be distributed in its entirety. The packages are also being constantly
updated by the loosely-managed developers, and the interest in a particular version of a package can be very
limited depending on the computer platforms and operating systems used.

In this paper, we propose a novel peer-to-peer assisted distribution system design that
addresses the above challenges. It enhances the existing distribution systems by providing compatible and yet more efficient downloading and updating services
for software packages. Our design leads to \texttt{apt-p2p}, a practical implementation that extends the popular \texttt{apt} distributor.  \texttt{apt-p2p}  has been used in conjuction with Debian-based distribution of Linux
software packages and will also be available in the next release of Ubuntu. We have addressed the key design issues in \texttt{apt-p2p}, including indexing table customization,
response time reduction, and multi-value extension. They together ensure
that the altruistic users' resources are effectively utilized and thus significantly reduces the currently
large bandwidth requirements of hosting the software, as confirmed by our existing real user statistics over the Internet.
\end{abstract}

@@

The existing distribution for free software is mostly based on the client/server model, e.g.,
the Advanced Package Tool (\texttt{apt}) for Linux \cite{apt}, which suffers from the well-known bottleneck problem.
Given the free nature of these software, there are often a number of users
motivated by altruism to help out with the distribution, so as to promote the healthy development
of this voluntary society.
We thus naturally expect that peer-to-peer distribution can be implemented in
this context, which will scale well with the currently large user bases and can easily explore the resources made available by
the volunteers.

Unfortunately, this application scenario has many unique characteristics, which
make a straightforward adoption of existing peer-to-peer systems for file sharing such as BitTorrent suboptimal. In particular,
there are too many packages to distribute each individually, but the archive is
too large to distribute in its entirety. The packages are also being constantly
updated by the loosely-managed developers, and the interest in a particular version of a package can be very
limited. They together make it very difficult to efficiently create and manage torrents/trackers. The random downloading nature of BitTorrent-like systems is also different from the
sequential order used in existing software package distributions. This in turn suppresses interaction with users
given the difficulty in tracking speed and downloading progress.

In this paper, we propose a novel peer-to-peer assisted distribution system design that
addresses the above challenges. It enhances the existing distribution systems by providing compatible and yet more efficient downloading and updating services
for software packages. Our design leads to the development of \texttt{apt-p2p}, a practical implementation based on the Debian \footnote{Debian - The Universal Operating System: {\it http://www.debian.org/}} package
distribution system.  We have addressed the key design issues in \texttt{apt-p2p}, including indexing table customization,
response time reduction, and multi-value extension. They together ensure
that the altruistic users' resources are effectively utilized and thus significantly reduces the currently
large bandwidth requirements of hosting the software.

\texttt{apt-p2p}  has been used in conjuction with Debian-based distribution of Linux
software packages and will also be available in the next release of Ubuntu. We have evaluated our current deployment  to
determine how effective it is at meeting our goals, and to see what
effect it is having on the Debian package distribution system. In particular, our existing real user statistics
have suggested that it responsively interacts with clients and substantially reduces server cost.

@@

\section{Background and Motivations}
\label{situation}

@@

Direct web downloading is also a common way, often coupled with a hash
verification file to be downloaded next to the desired
file. The hash file usually has the same file name, but with an
added extension identifying the hash used (e.g. \texttt{.md5} for
the MD5 hash). This type of file downloading and verification is
typical of free software hosting facilities that are open to anyone
to use, such as SourceForge.

@@

While it seems straightforward to use an existing peer-to-peer file sharing tool like BitTorrent for
free software package distribution, there are indeed a series of new challenges in this unique scenario:

@@

\subsection{System Overview}
Our model for using peer-to-peer to enhance package distribution is shown in
Figure~\ref{model}. As shown in Phase~1, our program will act as a
proxy (1,2), downloading (3) and caching all files communicated
between the user and the server (4). It will therefore also have
available the index files containing the cryptographic hashes all
packages. Later, in Phase~2, upon receiving a request from the user
to download a package (5), our program will search the index files
for the package being requested and find its hash (6). This hash can
then be looked up recursively in an indexing structure (a Distributed Hash Table, or DHT \cite{kademlia}, in our implementation) (7), which will return a
list of peers that have the package already (8). The package can
then be downloaded from the peers (11,12), it can be verified using
the hash (13), and if valid can be returned to the user (14). The
current nodes location is also added to the DHT for that hash (15),
as it is now a source for others to download from.

In steps (11,12), the fact that this package is also available to download for free
from a server is very important to our proposed model. If the package hash
can not be found in the DHT, the peer can then fallback to
downloading from the original location (i.e. the server).
The server thus, with no modification to its
functionality, serves as a seed for the packages in the peer-to-peer
system. Any packages that have just been updated, or that are very
rare, and so do not have any peers available, can always be found on
the server. Once the peer has completed the download from the server
and verified the package, it can then add itself to the DHT as the
first peer for the new package, so that future requests for the package
will not need the server.

@@

Note that, despite downloading the package from untrustworthy peers,
the trust of the package is always guaranteed through the use
of the cryptographic hashes. Nothing can be downloaded from a peer
until the hash is looked up in the DHT, so a hash must first come
from a trusted source (i.e. the distributors server). Most distributors use index
files that contain hashes for a large number of the packages in
their archive, and which are also hashed. After retrieving the
index's hash from the server, the index file can be downloaded from
peers and verified. Then the program has access to all the hashes of
the packages it will be downloading, all of which can be verified
with a \emph{chain of trust} that stretches back to the original
distributor's server.

@@

We created a customized DHT based on Khashmir \cite{khashmir}, which
is an implementation of Kademlia \cite{kademlia}. Khashmir is also the same DHT
implementation used by most of the existing BitTorrent clients to
implement trackerless operation. The communication is all handled by
UDP messages, and RPC (remote procedure call) requests and responses
are all \emph{bencoded} in the same way as BitTorrent's
\texttt{.torrent} files.
% Khashmir uses the high-level Twisted
% event-driven networking engine \cite{twisted}, so we also use
% Twisted in our sample implementation for all other networking needs.
More details of this customized DHT can be found below in
Section~\ref{custom_dht}.

Downloading is accomplished by sending simple HTTP requests to the
peers identified by lookups in the DHT to have the desired file.
Requests for a package are made using the package's hash, properly
encoded, as the URL to request from the peer. The HTTP server used
for the proxy also doubles as the server listening for requests for
downloads from other peers. All peers support HTTP/1.1, both in the
server and the client, which allows for pipelining of multiple
requests to a peer, and the requesting of smaller pieces of a large
file using the HTTP Range request header. Like in \texttt{apt},
SHA1 hashes are then used to verify downloaded files, including the large
index files that contain the hashes of the individual packages.

@@

The Kademlia DHT, like most other DHTs, assigns IDs to peers randomly from
the same space that is used for keys. The peers with IDs closest to
the desired key will then store the values for that key.
Nodes support four primitive requests.
\texttt{ping} will cause a peer to return nothing, and is only used
to determine if a node is still alive. \texttt{store} tells a
node to store a value associated with a given key. The most
important primitives are \texttt{find\_node} and
\texttt{find\_value}, which both function recursively to find nodes
close to a key. The queried nodes will return a list of the nodes
they know about that are closest to the key, allowing the querying
node to quickly traverse the DHT to find the nodes closest to the
desired key. The only difference between \texttt{find\_node} and \texttt{find\_value} is that the
\texttt{find\_value} query will cause a node to return a value, if
it has one for that key, instead of a list of nodes.

@@

Instead, the peers will store the torrent string for large files
separately in the DHT, and only contain a reference to it in their
stored value for the hash of the file. The reference is an SHA1 hash
of the entire concatenated length of the torrent string. If the
torrent string is short enough to store in the DHT (i.e. less than
1472 bytes, or about 70 pieces for the SHA1 hash), then a lookup of
that hash in the DHT will return the torrent string. Otherwise, a
request to the peer for the hash (using the same method as file
downloads, i.e. HTTP), will cause the peer to return the torrent
string.

Figure \ref{size_CDF} shows the size of the 22,298 packages
available in Debian in January 2008. We can see that most of the
packages are quite small, and so most will therefore not require
piece hash information to download. We have chosen a piece
size of 512 kB, which means that 17,515 (78\%) of the packages will
not require this information. There are 3054 packages that will
require 2 to 4 pieces, for which the torrent string can be stored
directly with the package hash in the DHT. There are 1667 packages
that will require a separate lookup in the DHT for the longer
torrent string as they require 5 to 70 pieces. Finally, there are
only 62 packages that require more than 70 pieces, and so will
require a separate request to a peer for the torrent string.

@@

We have also added some improvements to the recursive
\texttt{find\_node} and \texttt{find\_value} queries to speed up the
process when nodes fail. If enough nodes have responded to the
current query such that there are many new nodes to query that are
closer to the desired key, then a stalled request to a node further
away will be dropped in favor of a new request to a closer node.
This has the effect of leap-frogging unresponsive nodes and
focussing attention on the nodes that do respond. We will also
prematurely abort a query while there are still oustanding requests,
if enough of the closest nodes have responded and there are no
closer nodes found. This prevents a far away unresponsive node from
making the query's completion wait for it to timeout.

@@

The original design of Kademlia specified that each key would have
only a single value associated with it. The RPC to find this value
was called \texttt{find\_value} and worked similarly to
\texttt{find\_node}, iteratively finding nodes with ID's closer to
the desired key. However, if a node had a value stored associated
with the searched for key, it would respond to the request with that
value instead of the list of nodes it knows about that are closer.

@@

% \subsection{\textbf{OPTIONAL}: BitTorrent's Improvements}
% \label{bittorrent_dht}
%
% In the several years that some BitTorrent clients have been using a
% Kademlia-based DHT for tracker-less operation, the developers have
% made many enhancements which we can take advantage of. One of the
% most important is a security feature added to stop malicious nodes
% from subscribing other nodes as downloaders. When a node issues a
% request to another node to store its download info for that key, it
% must include a \emph{token} returned by the storing node in a recent
% \texttt{find\_node} request. The token is created by hashing the IP
% address of the requesting peer with a temporary secret that expires
% after several minutes. This prevents the requesting peer from faking
% its IP address in the store request, since it must first receive a
% response from a \texttt{find\_node} on that IP.
%
% We also made some BitTorrent-inspired changes to the parameters of
% the DHT originally specified by the authors of Kademlia. Since, as
% we will show later, peers stay online in our system for much longer
% periods of time, we reduced Kademlia's \emph{k} value from 20 to 8.
% The value is supposed to be large enough such that any given
% \emph{k} nodes are unlikely to fail within an hour of each other,
% which is very unlikely in our system given the long uptimes of
% nodes (see Figure~\ref{duration_online_1} in Section~\ref{analysis}.
% We also increased the number of concurrent outstanding
% requests allowed from 3 to 6 to speed up the recursive key finding
% processes.
%
% \subsection{\textbf{OPTIONAL}: Other Changes}
% \label{other_changes}
%
% In addition, we have allowed peers to store values in the DHT, even
% if the hash they are using is not the correct length. Most of the
% keys used in the DHT are based on the SHA1 hash, and so they are 20
% bytes in length. However, some files in the targetted Debian package
% system are only hashed using the MD5 algorithm, and so the hashes
% retrieved from the server are 16 bytes in length. The DHT will still
% store values using these keys by padding the end of them with zeroes
% to the proper length, as the loss of uniqueness from the 4 less
% bytes is not an issue. Also, the DHT will happily store hashes that
% are longer than 20 bytes, such as those from the 32 byte SHA256
% algorithm, by truncating them to the correct length. Since the
% requesting peer will have the full length of the hash, this will not
% affect its attempt to verify the downloaded file.

@@

Our \texttt{apt-p2p} implementation supporting the Debian package
distribution system has been available to all Debian users since May
3rd, 2008 \cite{apt-p2p-debian}, and will also be available in the
next release of Ubuntu \cite{apt-p2p-ubuntu}. We have since created
a \emph{walker} that will navigate the DHT and find all the peers
currently connected to it. This allows us to analyze many aspects of
our implementation in the real Internet environment.

@@

We first began analyzing the DHT on June 24th, and continue to this
day, giving us 2 months of data so far. Figure~\ref{walker_peers}
shows the number of peers we have seen in the DHT during this time.
The peer population is very steady, with just over 50 regular users
participating in the DHT at any time. We also note that we find 100
users who connect regularly (weekly), and we have found 186 unique
users in the 2 months of our analysis.

We also determined which users are
behind a firewall or NAT, which is one of the main problems of
implementing a peer-to-peer network. These peers will be
unresponsive to DHT requests from peers they have not contacted
recently, which will cause the peer to wait for a timeout to occur
(currently 9 seconds) before moving on. They will also be
unable to contribute any upload bandwidth to other peers, as all
requests for packages from them will also timeout. From
Figure~\ref{walker_peers}, we see that approximately half of all
peers suffered from this restriction. To address this problem, we added one other new RPC request that nodes can make:
\texttt{join}. This request is only sent on first loading the DHT,
and is usually only sent to the bootstrap nodes that are listed for
the DHT. These bootstrap nodes will respond to the request with the
requesting peer's IP and port, so that the peer can determine what
its oustide IP address is and whether port translation is being
used. In the future, we hope to add functionality similar to STUN
\cite{STUN}, so that nodes can detect whether they are NATted and
take appropriate steps to circumvent it.

@@

On July 31st we enhanced our walker to retrieve additional
information from each contacted peer. The peers are configured, by
default, to publish some statistics on how much they are downloading
and uploading, and their measured response times for DHT queries.
Our walker can extract this information if the peer is not
firewalled or NATted, it has not disabled this functionality, and if
it uses the same port for both its DHT (UDP) requests and download
(TCP) requests (which is also the default configuration parameter).

@@

In this paper, we have provided strong evidence that free software package distribution
and update exhibit many distinct characteristics, which call for new designs other
than the existing peer-to-peer systems for file sharing. To this end, we have
present \texttt{apt-p2p}, a novel peer-to-peer distributor that sits between
client and server, providing efficient and transparent downloading and updating services
for software packages. We have addressed the key design issues in \texttt{apt-p2p}, including DHT customization,
response time reduction, and multi-value extension. \texttt{apt-p2p}  has been used in conjuction with Debian-based distribution of Linux
software packages and will also be available in the next release of Ubuntu. Existing real user statistics
have suggested that it interacts well with clients and substantially reduces server cost.

>>>>

\begin{abstract}
The Internet has become a cost-effective
vehicle for software development and release, particular in the free software community.
Given the free nature of this software, there are often a number of users
motivated by altruism to help out with the distribution, so as to promote the healthy development
of this voluntary society. It is thus naturally expected that a peer-to-peer distribution can be implemented,
which will scale well with large user bases, and can easily explore the network resources made available by
the volunteers.

Unfortunately, this application scenario has many unique characteristics, which
make a straightforward adoption of existing peer-to-peer systems for file sharing (such as BitTorrent) suboptimal. In particular,
a software release often consists of a large number of packages, which are difficult to distribute individually, but the archive is
too large to be distributed in its entirety. The packages are also being constantly
updated by the loosely-managed developers, and the interest in a particular version of a package can be very
limited depending on the computer platforms and operating systems used.

In this paper, we propose a novel peer-to-peer assisted distribution system design that
addresses the above challenges. It enhances the existing distribution systems by providing compatible and yet more efficient downloading and updating services
for software packages. Our design leads to \texttt{apt-p2p}, a practical implementation that extends the popular \texttt{apt} distributor.  \texttt{apt-p2p}  has been used in conjunction with Debian-based distribution of Linux
software packages and is also available in the latest release of Ubuntu. We have addressed the key design issues in \texttt{apt-p2p}, including indexing table customization,
response time reduction, and multi-value extension. They together ensure
that the altruistic users' resources are effectively utilized and thus significantly reduces the currently
large bandwidth requirements of hosting the software, as confirmed by our existing real user statistics gathered over the Internet.
\end{abstract}

@@

The existing distribution for free software is mostly based on the client/server model, e.g.,
the Advanced Package Tool (\texttt{apt}) for Linux \cite{apt}, which suffers from the well-known bottleneck problem.
Given the free nature of this software, there are often a number of users
motivated by altruism to help out with the distribution, so as to promote the healthy development
of this voluntary society.
We thus naturally expect that peer-to-peer distribution can be implemented in
this context, which will scale well with the currently large user bases and can easily explore the resources made available by
the volunteers.

Unfortunately, this application scenario has many unique characteristics, which
make a straightforward adoption of existing peer-to-peer systems for file sharing (such as BitTorrent) suboptimal. In particular,
there are too many packages to distribute each individually, but the archive is
too large to distribute in its entirety. The packages are also being constantly
updated by the loosely-managed developers, and the interest in a particular version of a package can be very
limited. They together make it very difficult to efficiently create and manage torrents and trackers. The random downloading nature of BitTorrent-like systems is also different from the
sequential order used in existing software package distributors. This in turn suppresses interaction with users
given the difficulty in tracking speed and downloading progress.

In this paper, we propose a novel peer-to-peer assisted distribution system design that
addresses the above challenges. It enhances the existing distribution systems by providing compatible and yet more efficient downloading and updating services
for software packages. Our design leads to the development of \texttt{apt-p2p}, a practical implementation based on the Debian\footnote{Debian - The Universal Operating System: {\it http://www.debian.org/}} package
distribution system.  We have addressed the key design issues in \texttt{apt-p2p}, including indexing table customization,
response time reduction, and multi-value extension. They together ensure
that the altruistic users' resources are effectively utilized and thus significantly reduces the currently
large bandwidth requirements of hosting the software.

\texttt{apt-p2p}  has been used in conjunction with the Debian-based distribution of Linux
software packages and is also available in the latest release of Ubuntu. We have evaluated our current deployment  to
determine how effective it is at meeting our goals, and to see what
effect it is having on the Debian package distribution system. In particular, our existing real user statistics
have suggested that it responsively interacts with clients and substantially reduces server cost.

@@

\section{Background and Motivation}
\label{situation}

@@

Direct web downloading by users is also common, often coupled with a hash
verification file to be downloaded next to the desired
file. The hash file usually has the same file name, but with an
added extension identifying the hash used (e.g. \texttt{.md5} for
the MD5 hash). This type of file downloading and verification is
typical of free software hosting facilities that are open to anyone
to use, such as SourceForge.

@@

While it seems straightforward to use an existing peer-to-peer file sharing tool like BitTorrent for
this free software package distribution, there are indeed a series of new challenges in this unique scenario:

@@

\subsection{System Overview}
Our model for using peer-to-peer to enhance package distribution is shown in
Figure~\ref{model}. As shown in Phase~1, our program will act as a
proxy (1,2), downloading (3) and caching all files communicated
between the user and the server (4). It will therefore also have
available the index files containing the cryptographic hashes of all
packages. Later, in Phase~2, upon receiving a request from the user
to download a package (5), our program will search the index files
for the package being requested and find its hash (6). This hash can
then be looked up recursively in an indexing structure (a Distributed Hash Table, or DHT \cite{kademlia}, in our implementation) (7), which will return a
list of peers that have the package already (8). Then, in Phase~3, the package
can be downloaded from the peers (11,12), it can be verified using
the hash (13), and if valid can be returned to the user (14). The
current node's location is also added to the DHT for that hash (15),
as it is now a source for others to download from.

In steps (11,12), the fact that this package is also available to download for free
from a server is very important to our proposed model. If the package hash
can not be found in the DHT, the peer can then fallback to
downloading from the original location (i.e. the server).
The server thus, with no modification to its
functionality, serves as a seed for the packages in the peer-to-peer
system. Any packages that have just been updated or that are very
rare, and so do not yet have any peers available, can always be found on
the server. Once the peer has completed the download from the server
and verified the package, it can then add itself to the DHT as the
first peer for the new package, so that future requests for the package
will not need to use the server.

@@

Note that, despite downloading the package from untrustworthy peers,
the trust of the package is always guaranteed through the use
of the cryptographic hashes. Nothing can be downloaded from a peer
until the hash is looked up in the DHT, so a hash must first come
from a trusted source (i.e. the distributor's server). Most distributors use index
files that contain hashes for a large number of the packages in
their archive, and which are also hashed. After retrieving the
index file's hash from the server, the index file can also be downloaded from
peers and verified. Then the program has access to all the hashes of
the packages it will be downloading, all of which can be verified
with a \emph{chain of trust} that stretches back to the original
distributor's server.

@@

We created a customized DHT based on Khashmir \cite{khashmir}, which
is an implementation of Kademlia \cite{kademlia}. Khashmir is also the same DHT
implementation used by most of the existing BitTorrent clients to
implement trackerless operation. The communication is all handled by
UDP messages, and RPC (remote procedure call) requests and responses between nodes
are all \emph{bencoded} in the same way as BitTorrent's
\texttt{.torrent} files.
% Khashmir uses the high-level Twisted
% event-driven networking engine \cite{twisted}, so we also use
% Twisted in our sample implementation for all other networking needs.
More details of this customized DHT can be found below in
Section~\ref{custom_dht}.

Downloading is accomplished by sending simple HTTP requests to the
peers identified by lookups in the DHT to have the desired file.
Requests for a package are made using the package's hash (properly
encoded) as the URL to request from the peer. The HTTP server used
for the proxy also doubles as the server listening for requests for
downloads from other peers. All peers support HTTP/1.1, both in the
server and the client, which allows for pipelining of multiple
requests to a peer, and the requesting of smaller pieces of a large
file using the HTTP Range request header. Like in \texttt{apt},
SHA1 hashes are then used to verify downloaded files, including the large
index files that contain the hashes of the individual packages.

@@

The Kademlia DHT, like most other DHTs, assigns Ids to peers randomly from
the same space that is used for keys. The peers with Ids closest to
the desired key will then store the values for that key.
Nodes support four primitive requests.
\texttt{ping} will cause a peer to return nothing, and is only used
to determine if a node is still alive. \texttt{store} tells a
node to store a value associated with a given key. The most
important primitives are \texttt{find\_node} and
\texttt{find\_value}, which both function recursively to find nodes
close to a key. The queried nodes will return a list of the nodes
they know about that are closest to the key, allowing the querying
node to quickly traverse the DHT to find the nodes closest to the
desired key. The only difference between \texttt{find\_node} and \texttt{find\_value} is that the
\texttt{find\_value} query will cause a node to return a value, if
it has one for that key, instead of a list of nodes.

@@

Instead, the peers will store the torrent string for large files
separately in the DHT, and only contain a reference to it in their
stored value for the hash of the file. The reference is an SHA1 hash
of the entire concatenated length of the torrent string. If the
torrent string is short enough to store separately in the DHT (i.e. less than
1472 bytes, or about 70 pieces for the SHA1 hash), then a lookup of
that hash in the DHT will return the torrent string. Otherwise, a
request to the peer for the hash (using the same method as file
downloads, i.e. HTTP), will cause the peer to return the torrent
string.

Figure \ref{size_CDF} shows the size of the 22,298 packages
available in Debian in January 2008. We can see that most of the
packages are quite small, and so most will therefore not require
piece hash information to download. We have chosen a piece
size of 512 kB, which means that 17,515 (78\%) of the packages will
not require this information. There are 3054 packages that will
require 2 to 4 pieces, for which the torrent string can be stored
directly with the package hash in the DHT. There are 1667 packages
that will require a separate lookup in the DHT for the longer
torrent string, as they require 5 to 70 pieces. Finally, there are
only 62 packages that require more than 70 pieces, and so will
require a separate request to a peer for the torrent string.

@@

We have also added some improvements to the recursive
\texttt{find\_node} and \texttt{find\_value} queries to speed up the
process when nodes fail. If enough nodes have responded to the
current query such that there are many new nodes to query that are
closer to the desired key, then a stalled request to a node further
away will be dropped in favor of a new request to a closer node.
This has the effect of leap-frogging unresponsive nodes and
focussing attention on the closer nodes that do respond. We will also
prematurely abort a query while there are still oustanding requests,
if enough of the closest nodes have responded and there are no
closer nodes found. This prevents a far away unresponsive node from
making the query's completion wait for it to timeout.

@@

The original design of Kademlia specified that each key would have
only a single value associated with it. The RPC to find this value
was called \texttt{find\_value} and worked similarly to
\texttt{find\_node}, iteratively finding nodes with Id's closer to
the desired key. However, if a node had a value stored associated
with the searched for key, it would respond to the request with that
value instead of the list of nodes it knows about that are closer.

@@

% \subsection{\textbf{OPTIONAL}: BitTorrent's Improvements}
% \label{bittorrent_dht}
%
% In the several years that some BitTorrent clients have been using a
% Kademlia-based DHT for tracker-less operation, the developers have
% made many enhancements which we can take advantage of. One of the
% most important is a security feature added to stop malicious nodes
% from subscribing other nodes as downloaders. When a node issues a
% request to another node to store its download info for that key, it
% must include a \emph{token} returned by the storing node in a recent
% \texttt{find\_node} request. The token is created by hashing the IP
% address of the requesting peer with a temporary secret that expires
% after several minutes. This prevents the requesting peer from faking
% its IP address in the store request, since it must first receive a
% response from a \texttt{find\_node} on that IP.
%
% We also made some BitTorrent-inspired changes to the parameters of
% the DHT originally specified by the authors of Kademlia. Since, as
% we will show later, peers stay online in our system for much longer
% periods of time, we reduced Kademlia's \emph{k} value from 20 to 8.
% The value is supposed to be large enough such that any given
% \emph{k} nodes are unlikely to fail within an hour of each other,
% which is very unlikely in our system given the long uptime of
% nodes (see Figure~\ref{duration_online_1} in Section~\ref{analysis}.
% We also increased the number of concurrent outstanding
% requests allowed from 3 to 6 to speed up the recursive key finding
% processes.
%
% \subsection{\textbf{OPTIONAL}: Other Changes}
% \label{other_changes}
%
% In addition, we have allowed peers to store values in the DHT, even
% if the hash they are using is not the correct length. Most of the
% keys used in the DHT are based on the SHA1 hash, and so they are 20
% bytes in length. However, some files in the targetted Debian package
% system are only hashed using the MD5 algorithm, and so the hashes
% retrieved from the server are 16 bytes in length. The DHT will still
% store values using these keys by padding the end of them with zeroes
% to the proper length, as the loss of uniqueness from the 4 less
% bytes is not an issue. Also, the DHT will happily store hashes that
% are longer than 20 bytes, such as those from the 32 byte SHA256
% algorithm, by truncating them to the correct length. Since the
% requesting peer will have the full length of the hash, this will not
% affect its attempt to verify the downloaded file.

@@

Our \texttt{apt-p2p} implementation supporting the Debian package
distribution system has been available to all Debian users since May
3rd, 2008 \cite{apt-p2p-debian}, and is also available in the
latest release of Ubuntu \cite{apt-p2p-ubuntu}. We created
a \emph{walker} that will navigate the DHT and find all the peers
currently connected to it. This allows us to analyze many aspects of
our implementation in the real Internet environment.

@@

We first began analyzing the DHT on June 24th, 2008, and continued
until we had gathered almost 2 months of data. Figure~\ref{walker_peers}
shows the number of peers we have seen in the DHT during this time.
The peer population is very steady, with just over 50 regular users
participating in the DHT at any time. We also note that we find 100
users who connect regularly (weekly), and we have found 186 unique
users in the 2 months of our analysis.

We also determined which users are
behind a firewall or NAT, which is one of the main problems of
implementing a peer-to-peer network. These peers will be
unresponsive to DHT requests from peers they have not contacted
recently, which will cause the peer to wait for a timeout to occur
(currently 9 seconds) before moving on. They will also be
unable to contribute any upload bandwidth to other peers, as all
requests for packages from them will also timeout. From
Figure~\ref{walker_peers}, we see that approximately half of all
peers suffered from this restriction. To address this problem, we added one other new RPC request that nodes can make:
\texttt{join}. This request is only sent on first loading the DHT,
and is usually only sent to the bootstrap nodes that are listed for
the DHT. These bootstrap nodes will respond to the request with the
requesting peer's IP and port, so that the peer can determine what
its outside IP address is and whether port translation is being
used. In the future, we hope to add functionality similar to STUN
\cite{STUN}, so that nodes can detect whether they are NATted and
take appropriate steps to circumvent it.

@@

On July 31st we enhanced our walker to retrieve additional
information from each contacted peer. The peers are configured, by
default, to publish some statistics on how much they are downloading
and uploading, and their measured response times for DHT queries.
Our walker can extract this information if the peer is not
firewalled or NATted, it has not disabled this functionality, and if
it uses the same port for both its DHT (UDP) requests and download
(TCP) requests (which is also the default configuration behavior).

@@

In this paper, we have provided strong evidence that free software package distribution
and update exhibit many distinct characteristics, which call for new designs other
than the existing peer-to-peer systems for file sharing. To this end, we have
presented \texttt{apt-p2p}, a novel peer-to-peer distributor that sits between
client and server, providing efficient and transparent downloading and updating services
for software packages. We have addressed the key design issues in \texttt{apt-p2p}, including DHT customization,
response time reduction, and multi-value extension. \texttt{apt-p2p}  has been used in conjunction with Debian-based distribution of Linux
software packages and is also available in the latest release of Ubuntu. Existing real user statistics
have suggested that it interacts well with clients and substantially reduces server cost.
